---
title: "100-generate-loci"
author: "Mac Campbell"
date: "June 23, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
library(ggtree)
library(phytools)
library(ggrepel)
```

## EPV Loci
We need to start with a list of loci using the Parvoviridae-GLUE repository.

```{r}
amdo<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/parvovirinae/epv-amdo-side-data.tsv") %>% 
    mutate(virus_genus="Amdoparvovirus")
  
dependo<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/parvovirinae//epv-dependo-side-data.tsv")
  
erythro<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/parvovirinae/epv-erythro-side-data.tsv") %>% 
    mutate(virus_genus="Erythroparvovirus")
  
proto<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/parvovirinae/epv-proto-side-data.tsv")  %>% 
    mutate(virus_genus="Protoparvovirus") %>% 
    mutate(organism=host_species) %>% select(-host_species)
  
ichthama<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/hamaparvovirinae/epv-ichthama-side-data.tsv") %>%
    mutate(virus_genus="Ichthamaparvovirus") %>%
   mutate(organism=host_species) %>% select(-host_species)
  
unc<-read_tsv("~/github/Parvoviridae-GLUE/tabular/eve/parvovirinae/epv-unc-parvo-side-data.tsv")%>%
    mutate(virus_genus="Unclassified") %>%
  mutate(organism=host_species) %>% select(-host_species)

#Need to have scyliorhinus in the tree, and tetraodon for unclassified parvoviruses
```

```{r}
data<-bind_rows(amdo,dependo,erythro,proto,ichthama,unc)
data$Species<-gsub("_"," ",data$organism)
data<-data %>% select(host_class, sequenceID, Species, organism, locus_name, virus_genus)
species<-data %>% select(Species) %>% unique()
write_tsv(species, "outputs/100/species-list-100.tsv", col_names = FALSE)
species2<-c(species$Species, "Homo sapiens") %>% as_tibble()
write_tsv(species2, "outputs/100/species-list-with-human-100.tsv", col_names = FALSE)
```

With time tree:
20 unresolved
Lonchura striata domestica (replaced with Lonchura striata)
Pelusios castaneus (replaced with Pelusios williamsi)
Panthera tigris altaica (replaced with Panthera tigris)
Prionailurus bengalensis euptilurus (replaced with Prionailurus bengalensis)
Canis lupus dingo (replaced with Canis lupus)
Canis familiaris (replaced with Canis lupus)
Equus asinus somalicus (replaced with Equus asinus)
Equus africanus asinus (replaced with Equus asinus)
Equus burchellii boehmi (replaced with Equus burchellii)
Equus zebra hartmannae (replaced with Equus zebra)
Ceratotherium simum cottoni (replaced with Ceratotherium simum)
Dicerorhinus sumatrensis sumatrensis (replaced with Dicerorhinus sumatrensis)
Cervus elaphus hippelaphus (replaced with Cervus elaphus)
Murina aurata feae (replaced with Murina aurata)
Mus castaneus (replaced with Mus musculus)
Peromyscus polionotus subgriseus (replaced with Peromyscus polionotus)
Peromyscus maniculatus bairdii (replaced with Peromyscus maniculatus)
Colobus angolensis palliatus (replaced with Colobus angolensis)
Emydocephalus ijimae (no substitute found)
Neophocaena asiaeorientalis (no substitute found)

We need to replace the names in our data frame or tip labels to resolve this problem. t$data will have "Ptyas_mucosa"
### Tree
```{r}
tree<-read.tree("outputs/100/species-list-100.nwk")

vec<-c("Lonchura_striata","Pelusios_williamsi","Dicerorhinus_sumatrensis","Murina_aurata",
       "Peromyscus_polionotus","Peromyscus_maniculatus","Colobus_angolensis", "Equus_zebra",
       "Cervus_elpahus", "Ceratotherium_simum","Dicerorhinus_sumatrensis", "Carlito_syrichta")
       
vec2<-c("Lonchura_striata_domestica","Pelusios_castaneus","Dicerorhinus_sumatrensis_sumatrensis","Murina_aurata_feae",
        "Peromyscus_polionotus_subgriseus","Peromyscus_maniculatus_bairdii","Colobus_angolensis_palliatus", "Equus_zebra_hartmannae",
        "Cervus_elaphus_hippelaphus","Ceratotherium_simum_cottoni", "Dicerorhinus_sumatrensis_sumatrensis","Tarsius_syrichta")

#This doesn't work how I think it would
#tree$tip.label<-replace(tree$tip.label, tree$tip.label %in% vec, vec2)
#As loop? 1:length(vec)
for (i in 1:length(vec)) {

tree$tip.label<-replace(tree$tip.label, tree$tip.label==vec[i], vec2[i])
  
}

t<-ggtree(tree)

#Making tip ages = 0 
t$data<-t$data %>% mutate(Age=max(x)-x)

t + geom_tiplab(size=2) +
  geom_treescale()+
  xlim(0,500)+
  geom_nodelab(aes(label=round(Age,2)), hjust=0, size=2)

ggsave("outputs/100/tree.pdf", width=8, height=24)
```

### Minimum Ages
```{r}
#Making "Taxa" for tip labs and calculate number of taxa
#Exlude unassigned "NK" locus_names
#filter to tips in tree
treetips<-t$data %>% filter(isTip==TRUE) %>% select(label)

df<-data %>% filter(locus_name != "NK") %>% unique() %>%
  mutate(Delim=gsub(" ","_",Species)) %>%
  filter(Delim %in% treetips$label) %>%
  group_by(locus_name) %>% mutate(Taxa=paste(Delim, collapse=" "))  %>% mutate(Count=n())

#getting min age of nodes
df2<-df %>% mutate(node = as.numeric(ifelse(Count > 1, findMRCA(tree, tips=strsplit(Taxa, " ")[[1]]), t$data[t$data$label==Taxa,]$node)))
df3<-left_join(df2, t$data, by="node")
df3<-df3 %>% mutate(Age=ifelse(Age < 1, 0, Age))
df3$Age<-replace_na(df3$Age, 0)

#Summarize min age of nodes
df3 %>% select(locus_name, Age) %>% unique()
```
Including tmrca to humans

```{r}
tree2<-read.tree("outputs/100/species-list-with-human-100.nwk")

for (i in 1:length(vec)) {

tree2$tip.label<-replace(tree2$tip.label, tree2$tip.label==vec[i], vec2[i])
  
}

t2<-ggtree(tree2)
t2$data<-t2$data %>% mutate(Age=max(x)-x)

dfh<-df %>% mutate(Taxa=paste0(Taxa, " Homo_sapiens")) %>%
  mutate(node = as.numeric(ifelse(Count >= 1, findMRCA(tree2, tips=strsplit(Taxa, " ")[[1]]), NA)))

dfh2<-left_join(dfh, t2$data, by="node") %>% rename(DivTime=Age)
dfh2$Taxa<-gsub(" Homo_sapiens","", dfh2$Taxa)
```


Combine (trees are different, so......)     
```{r}
df4<-df3 %>% left_join(dfh2 %>% select(sequenceID, Species, organism, locus_name, virus_genus, Taxa, DivTime))

df5<-df4 %>% select(locus_name, virus_genus, Age, DivTime) %>% unique() %>% rename(`Minimum Age` = Age, `Divergence Time From Humans`=DivTime)
df5

write_csv(df5, "outputs/100/all-loci-ages.csv")
```

Now to merge with other data:

```{r}
table<-read_csv("meta/eve-meta-hg38-05032021.csv") %>% left_join(df5, by=c("EVE"="locus_name")) %>% select(-Orientation)

write_csv(table, "meta/full-table.csv")
```

## Body Size
Not for this project, but most conveniently done here. https://figshare.com/articles/dataset/Full_Archive/3531875?backTo=/collections/PanTHERIA_a_species-level_database_of_life_history_ecology_and_geography_of_extant_and_recently_extinct_mammals/3301274 


```{r}
pan<-read_tsv("outputs/100/3531875/ECOL_90_184/PanTHERIA_1-0_WR05_Aug2008.txt", na = c("-999", "-999.00"))
```

Create a column to join on and select body size     
organism="genus_species"
Species="genus species"
```{r}
pan2<-pan %>% mutate(organism=paste0(MSW05_Genus,"_",MSW05_Species), Species=MSW05_Binomial) %>%
                       select(organism, Species,`5-1_AdultBodyMass_g`) %>% 
                       rename(`Body Mass (g)`=`5-1_AdultBodyMass_g`)

```

```{r}
ggplot(pan2)+
  geom_histogram(aes(x=log10(`Body Mass (g)`)))
```

Add to tree     
```{r}
t %<+% pan2 +
  geom_tippoint(aes(color=log10(`Body Mass (g)`)))+
  scale_color_viridis_c(direction = -1) 

```

Now, let's count up the number of loci/organism,

```{r}
counts<-data %>% group_by(organism) %>% summarize(Count=n())

t %<+% left_join(pan2,counts) +
  geom_tiplab(offset = 30, size=1) +
  geom_tippoint(aes(color=log10(`Body Mass (g)`)), pch=15)+
  geom_tippoint(aes(x=x+20, size=Count), alpha=0.75) +
  scale_color_viridis_c(direction = -1) +
  xlim(0,500)
ggsave("outputs/100/tree-with-mass.pdf", height=24, width=8)

```

```{r}
surveyed<-read_csv("~/github/Parvoviridae-GLUE/digs/vertebrate-genomes-screened.csv")
temp<-left_join(pan2, surveyed) %>% na.omit() %>% left_join(counts)
temp$Count<-replace_na(temp$Count, 0)
rels<-temp %>% mutate(LogMass=log10(`Body Mass (g)`))

#https://stackoverflow.com/questions/37329074/geom-smooth-and-exponential-fits
exp.model <-lm(Count ~ exp(-LogMass), rels)
lm<-lm(Count~LogMass, rels)
ggplot(rels) +
  geom_point(aes(x=LogMass, y=Count)) +
 # geom_smooth(method="lm", aes(x=LogMass, y=Count, color="Exp Model"), formula= (y ~ exp(-x)), 
      #        se=FALSE, linetype = 1) +
  geom_smooth(aes(x=LogMass, y=Count), method="lm", formula=(y~x))

```
