---
title: "208-over-rep"
output: html_document
date: "2023-07-06"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library("tidyverse")
library("clusterProfiler")
library("ggupset")
library("msigdbr")
library("org.Hs.eg.db")
library("magrittr")
```
    

#Need a list of genes and a list of background genes    
```{r}
up<-read_csv("outputs/206/genes-found-across-comparisions.csv") %>% filter(Direction=="Positive")
down<-read_csv("outputs/206/genes-found-across-comparisions.csv") %>% filter(Direction=="Negative")
```


```{r}
hs_msigdb_df <- msigdbr(species = "Homo sapiens")
# Filter the human data frame to the KEGG pathways that are included in the
# curated gene sets
hs_kegg_df <- hs_msigdb_df %>%
  dplyr::filter(
    gs_cat == "C2", # This is to filter only to the C2 curated gene sets
    gs_subcat == "CP:KEGG" # This is because we only want KEGG pathways
  )
```
  
setting up background set with rowsums >= 10 as in DE analysis
```{r}
interest<-up$Gene
backgroundset <- read_csv("data/raw_counts-intronic-intergenic.csv") %>% 
  dplyr::select(-Gene.name) %>% mutate(Sum=rowSums(across(where(is.numeric)))) %>%
  filter(Sum >= 10)
```

```{r}
kegg_ora_results <- enricher(
  gene = interest, # A vector of your genes of interest
  pvalueCutoff = 0.1, # Can choose a FDR cutoff
  pAdjustMethod = "BH", # Method to be used for multiple testing correction
  universe = backgroundset$ID, # A vector containing your background set genes
  # The pathway information should be a data frame with a term name or
  # identifier and the gene identifiers
  TERM2GENE = dplyr::select(
    hs_kegg_df,
    gs_name,
    human_ensembl_gene
  )
)
kegg_ora_results$Description

```

```{r}
kegg_ora_results_down <- enricher(
  gene = down$Gene, # A vector of your genes of interest
  pvalueCutoff = 0.1, # Can choose a FDR cutoff
  pAdjustMethod = "BH", # Method to be used for multiple testing correction
  universe = backgroundset$ID, # A vector containing your background set genes
  # The pathway information should be a data frame with a term name or
  # identifier and the gene identifiers
  TERM2GENE = dplyr::select(
    hs_kegg_df,
    gs_name,
    human_ensembl_gene
  )
)
kegg_ora_results_down$Description
```

Down are Control
 $ ID         : chr  "KEGG_ASTHMA" "KEGG_INTESTINAL_IMMUNE_NETWORK_FOR_IGA_PRODUCTION" "KEGG_GRAFT_VERSUS_HOST_DISEASE" "KEGG_HEMATOPOIETIC_CELL_LINEAGE" ...
 $ Description: chr  "KEGG_ASTHMA" "KEGG_INTESTINAL_IMMUNE_NETWORK_FOR_IGA_PRODUCTION" "KEGG_GRAFT_VERSUS_HOST_DISEASE" "KEGG_HEMATOPOIETIC_CELL_LINEAGE" ..
 
 This is interesting... Making plots     
 
```{r}
enrich_plot <- enrichplot::dotplot(kegg_ora_results_down)

enrich_plot
```
     
     
```{r}
upset_plot <- enrichplot::upsetplot(kegg_ora_results_down)
upset_plot
```


