---
title: "301-salmon"
output: html_document
date: "2024-09-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

Probably best to go and get the TPM counts with salmon

Available module: salmon/1.10.1

Retrieving hg38 transcripts into data/salmon

https://ftp.ensembl.org/pub/release-112/fasta/homo_sapiens/cdna/Homo_sapiens.GRCh38.cdna.all.fa.gz
gunzip Homo_sapiens.GRCh38.cdna.all.fa.gz
cat Homo_sapiens.GRCh38.cdna.all.fa GFP.fasta  > human.fasta

module load salmon


srun -p high -t 4:00:00 --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=8 salmon index -t human.fasta -i human_index

#!/bin/bash
for fn in data/DRR0161{25..40};
do
samp=`basename ${fn}`
echo "Processing sample ${samp}"
salmon quant -i athal_index -l A \
         -1 ${fn}/${samp}_1.fastq.gz \
         -2 ${fn}/${samp}_2.fastq.gz \
         -p 8 --validateMappings -o quants/${samp}_quant
done 

```{sh, eval=FALSE}
srun -p med -t 72:00:00 --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=8 \
salmon quant -i data/salmon/human_index -l A \
-1 data/donors-1-2/AAVS1-1_R1_001.fastq.gz \
-2 data/donors-1-2/AAVS1-1_R2_001.fastq.gz \
-p 8 ==validateMappings -o outputs/301/AAVS1-Donor.1 
```

Working command!

generate more commands:     

```{r}
seqs<-read_csv("meta/rna-seq-meta-for-align.csv") 
seqs %>% mutate(Command = paste0("srun -p med -t 72:00:00 --mem=32G --nodes=1 --ntasks-per-node=1 --cpus-per-task=8 salmon quant -i data/salmon/human_index -l A -1 ",Location, "/",Seqfile1, " -2 ",Location, "/",Seqfile2,
                                  " -p 8  ==validateMappings -o outputs/301/",`NCBI Sample Name`, " &")) %>% select(Command) %>% write_tsv("301.1-commands.tsv")
```

seems to have worked! Have a bunch of quant.sf files

ls > samples.txt
mkdir temp
for sample in `cat samples.txt`; do \
    echo ${sample}
    cat ${sample}/quant.sf | tail -n +1 | cut -f 4 >temp/${sample}.count
done;
cut -f 1 AAVS1-Donor.1/quant.sf |  tail -n +1 > temp/gene-names.txt
paste temp/gene-names.txt temp/*.count > temp/temp.temp

cat <(paste -s samples.txt ) temp/temp.temp  > combined-counts.txt 

scp farm:~/epv-safe-harbor/outputs/301/combined-c* .

```{r}
df<-read_tsv("outputs/301/combined-counts.txt")
df %>% filter(Gene=="ENSG0000000000") %>% write_csv("outputs/301/gsh-tpms.csv")
```